---
title: "Data Workbench"
output:
  html_document:
    includes:
      after_body: footer.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(readr)
library(jsonlite)

# Load all CSV data
creatures <- read_csv("creatures.csv", show_col_types = FALSE)
lairs <- read_csv("lairs.csv", show_col_types = FALSE)
lair_mobiles <- read_csv("lair_mobiles.csv", show_col_types = FALSE)
lair_spawn_groups <- read_csv("lair_spawn_groups.csv", show_col_types = FALSE)
static_spawns <- read_csv("static_spawns.csv", show_col_types = FALSE)
zones <- read_csv("zones.csv", show_col_types = FALSE)

# Get column info for schema display
get_schema <- function(df, name) {
  cols <- sapply(names(df), function(col) {
    paste0(col, " (", class(df[[col]])[1], ")")
  })
  list(name = name, columns = as.list(cols), row_count = nrow(df))
}

schema_info <- list(
  creatures = get_schema(creatures, "creatures"),
  lairs = get_schema(lairs, "lairs"),
  lair_mobiles = get_schema(lair_mobiles, "lair_mobiles"),
  lair_spawn_groups = get_schema(lair_spawn_groups, "lair_spawn_groups"),
  static_spawns = get_schema(static_spawns, "static_spawns"),
  zones = get_schema(zones, "zones")
)
```

# SQL Data Workbench

Query the SWGEmu creature data using SQL. All data is loaded into an in-browser SQLite database powered by [SQL.js](https://sql.js.org/).

## How to Use

1. Write your SQL query in the editor below
2. Click **Run Query** (or press Ctrl+Enter)
3. Results appear in the table below
4. Use the **Schema Reference** to see available tables and columns

<style>
#workbench-container {
  display: grid;
  grid-template-columns: 300px 1fr;
  gap: 20px;
  margin: 20px 0;
}
#schema-panel {
  background: #f5f5f5;
  padding: 15px;
  border-radius: 5px;
  max-height: 600px;
  overflow-y: auto;
}
#schema-panel h3 { margin-top: 0; }
.schema-table {
  margin-bottom: 15px;
  background: white;
  padding: 10px;
  border-radius: 3px;
  border: 1px solid #ddd;
}
.schema-table h4 {
  margin: 0 0 5px 0;
  color: #333;
  cursor: pointer;
}
.schema-table h4:hover { color: #0066cc; }
.schema-table .row-count {
  font-size: 12px;
  color: #666;
  margin-bottom: 5px;
}
.schema-table ul {
  margin: 0;
  padding-left: 20px;
  font-size: 13px;
  font-family: monospace;
}
.schema-table li { margin: 2px 0; }
#query-panel { }
#sql-editor {
  width: 100%;
  height: 150px;
  font-family: monospace;
  font-size: 14px;
  padding: 10px;
  border: 1px solid #ccc;
  border-radius: 4px;
  resize: vertical;
}
#sql-editor:focus {
  outline: none;
  border-color: #3388ff;
}
#query-controls {
  margin: 10px 0;
}
#run-query {
  padding: 10px 20px;
  font-size: 14px;
  background: #3388ff;
  color: white;
  border: none;
  border-radius: 4px;
  cursor: pointer;
}
#run-query:hover { background: #2266dd; }
#run-query:disabled { background: #ccc; cursor: not-allowed; }
#query-status {
  margin-left: 15px;
  color: #666;
}
#query-error {
  color: #cc0000;
  background: #fff0f0;
  padding: 10px;
  border-radius: 4px;
  margin: 10px 0;
  display: none;
}
#results-container {
  margin-top: 20px;
  overflow-x: auto;
}
#results-table {
  width: 100%;
  border-collapse: collapse;
  font-size: 13px;
}
#results-table th, #results-table td {
  border: 1px solid #ddd;
  padding: 8px;
  text-align: left;
}
#results-table th {
  background: #f5f5f5;
  font-weight: bold;
}
#results-table tr:nth-child(even) { background: #fafafa; }
#results-table tr:hover { background: #f0f0f0; }
#example-queries {
  margin: 20px 0;
}
.example-query {
  background: #f9f9f9;
  padding: 10px;
  margin: 10px 0;
  border-radius: 4px;
  border-left: 3px solid #3388ff;
}
.example-query h5 { margin: 0 0 5px 0; }
.example-query code {
  display: block;
  background: #fff;
  padding: 8px;
  font-size: 12px;
  cursor: pointer;
  border-radius: 3px;
}
.example-query code:hover { background: #e8f4ff; }
#loading-indicator {
  text-align: center;
  padding: 40px;
  font-size: 18px;
  color: #666;
}
</style>

```{r workbench_html, results='asis', echo=FALSE}
cat('<div id="loading-indicator">Loading SQL.js and data... Please wait.</div>
<div id="workbench-container" style="display:none;">
<div id="schema-panel"><h3>Schema Reference</h3><p style="font-size:12px;color:#666;">Click table name to insert into query</p><div id="schema-list"></div></div>
<div id="query-panel"><h3>SQL Query</h3><textarea id="sql-editor" placeholder="Enter your SQL query here...">SELECT creatureName, level, baseHAM, armor
FROM creatures
WHERE armor > 0
ORDER BY level
LIMIT 20</textarea><div id="query-controls"><button id="run-query" onclick="runQuery()">Run Query</button><span id="query-status"></span></div><div id="query-error"></div><div id="results-container"><table id="results-table"></table></div></div>
</div>')
```

## Example Queries

<div id="example-queries">
<div class="example-query">
<h5>Lowest level creatures with armor</h5>
<code onclick="loadExample(this)">SELECT creatureName, level, armor, kinetic, energy
FROM creatures
WHERE armor > 0
ORDER BY level
LIMIT 15</code>
</div>

<div class="example-query">
<h5>Creatures with highest HAM per level (outliers)</h5>
<code onclick="loadExample(this)">SELECT creatureName, level, baseHAM,
       ROUND(CAST(baseHAM AS FLOAT) / level, 1) as ham_per_level
FROM creatures
WHERE level > 0
ORDER BY ham_per_level DESC
LIMIT 20</code>
</div>

<div class="example-query">
<h5>Creatures with special resists (effective resists)</h5>
<code onclick="loadExample(this)">SELECT creatureName, level,
       kinetic, energy, heat, cold, electricity, acid
FROM creatures
WHERE kineticEffective = 1 OR energyEffective = 1
ORDER BY level DESC
LIMIT 20</code>
</div>

<div class="example-query">
<h5>All creatures in a specific spawn zone</h5>
<code onclick="loadExample(this)">SELECT DISTINCT c.creatureName, c.level, c.socialGroup, z.planet
FROM creatures c
JOIN lair_mobiles lm ON c.creatureName = lm.creatureName
JOIN lair_spawn_groups lsg ON lm.lairName = lsg.lairTemplateName
JOIN zones z ON lsg.spawnGroupName = z.spawnZone
WHERE z.spawnZone = 'corellia_easy_nw'
ORDER BY c.level</code>
</div>

<div class="example-query">
<h5>Count creatures by social group</h5>
<code onclick="loadExample(this)">SELECT socialGroup, COUNT(*) as count,
       ROUND(AVG(level), 1) as avg_level,
       MIN(level) as min_level, MAX(level) as max_level
FROM creatures
GROUP BY socialGroup
ORDER BY count DESC</code>
</div>

<div class="example-query">
<h5>Planets with most static spawns</h5>
<code onclick="loadExample(this)">SELECT zone_id as planet, COUNT(*) as spawn_count,
       COUNT(DISTINCT mobile) as unique_creatures
FROM static_spawns
GROUP BY zone_id
ORDER BY spawn_count DESC</code>
</div>

<div class="example-query">
<h5>Creatures that appear in multiple planets</h5>
<code onclick="loadExample(this)">SELECT c.creatureName, COUNT(DISTINCT z.planet) as planet_count,
       GROUP_CONCAT(DISTINCT z.planet) as planets
FROM creatures c
JOIN lair_mobiles lm ON c.creatureName = lm.creatureName
JOIN lair_spawn_groups lsg ON lm.lairName = lsg.lairTemplateName
JOIN zones z ON lsg.spawnGroupName = z.spawnZone
GROUP BY c.creatureName
HAVING planet_count > 1
ORDER BY planet_count DESC
LIMIT 20</code>
</div>

<div class="example-query">
<h5>Resource yields by creature</h5>
<code onclick="loadExample(this)">SELECT creatureName, level,
       meatType, meatAmount,
       hideType, hideAmount,
       boneType, boneAmount,
       milkType, milkAmount
FROM creatures
WHERE meatAmount > 0 OR hideAmount > 0 OR boneAmount > 0
ORDER BY level
LIMIT 30</code>
</div>
</div>

```{r embed_data, results='asis', echo=FALSE}
# Embed all data as JSON for JavaScript to load
cat(sprintf("
<script>
var csvData = {
  creatures: %s,
  lairs: %s,
  lair_mobiles: %s,
  lair_spawn_groups: %s,
  static_spawns: %s,
  zones: %s
};

var schemaInfo = %s;
</script>
",
  toJSON(creatures, dataframe = "rows"),
  toJSON(lairs, dataframe = "rows"),
  toJSON(lair_mobiles, dataframe = "rows"),
  toJSON(lair_spawn_groups, dataframe = "rows"),
  toJSON(static_spawns, dataframe = "rows"),
  toJSON(zones, dataframe = "rows"),
  toJSON(schema_info, auto_unbox = TRUE)
))
```

<script src="https://cdnjs.cloudflare.com/ajax/libs/sql.js/1.8.0/sql-wasm.js"></script>

<script>
var db = null;

// Initialize SQL.js and load data
async function initDatabase() {
  try {
    // Initialize SQL.js
    const SQL = await initSqlJs({
      locateFile: file => `https://cdnjs.cloudflare.com/ajax/libs/sql.js/1.8.0/${file}`
    });

    db = new SQL.Database();

    // Create tables and load data
    loadTable('creatures', csvData.creatures);
    loadTable('lairs', csvData.lairs);
    loadTable('lair_mobiles', csvData.lair_mobiles);
    loadTable('lair_spawn_groups', csvData.lair_spawn_groups);
    loadTable('static_spawns', csvData.static_spawns);
    loadTable('zones', csvData.zones);

    // Build schema display
    buildSchemaPanel();

    // Show workbench
    document.getElementById('loading-indicator').style.display = 'none';
    document.getElementById('workbench-container').style.display = 'grid';

    // Run initial query
    runQuery();

  } catch (err) {
    document.getElementById('loading-indicator').innerHTML =
      '<span style="color:red;">Error loading SQL.js: ' + err.message + '</span>';
  }
}

function loadTable(tableName, rows) {
  if (!rows || rows.length === 0) return;

  // Get column names and types from first row
  var columns = Object.keys(rows[0]);

  // Infer types from data
  var colDefs = columns.map(function(col) {
    var sampleVal = rows[0][col];
    var type = 'TEXT';
    if (typeof sampleVal === 'number') {
      type = Number.isInteger(sampleVal) ? 'INTEGER' : 'REAL';
    }
    return '"' + col + '" ' + type;
  }).join(', ');

  // Create table
  var createSQL = 'CREATE TABLE "' + tableName + '" (' + colDefs + ')';
  db.run(createSQL);

  // Insert rows
  var placeholders = columns.map(function() { return '?'; }).join(', ');
  var insertSQL = 'INSERT INTO "' + tableName + '" VALUES (' + placeholders + ')';
  var stmt = db.prepare(insertSQL);

  rows.forEach(function(row) {
    var values = columns.map(function(col) {
      var val = row[col];
      return val === null || val === undefined ? null : val;
    });
    stmt.run(values);
  });

  stmt.free();
}

function buildSchemaPanel() {
  var html = '';
  Object.keys(schemaInfo).forEach(function(tableName) {
    var table = schemaInfo[tableName];
    html += '<div class="schema-table">';
    html += '<h4 onclick="insertTableName(\'' + tableName + '\')">' + tableName + '</h4>';
    html += '<div class="row-count">' + table.row_count + ' rows</div>';
    html += '<ul>';
    // table.columns is an object, not an array - use Object.values
    Object.values(table.columns).forEach(function(col) {
      html += '<li>' + col + '</li>';
    });
    html += '</ul></div>';
  });
  document.getElementById('schema-list').innerHTML = html;
}

function insertTableName(tableName) {
  var editor = document.getElementById('sql-editor');
  var pos = editor.selectionStart;
  var text = editor.value;
  editor.value = text.slice(0, pos) + tableName + text.slice(pos);
  editor.focus();
  editor.selectionStart = editor.selectionEnd = pos + tableName.length;
}

function runQuery() {
  if (!db) return;

  var sql = document.getElementById('sql-editor').value.trim();
  if (!sql) return;

  var errorDiv = document.getElementById('query-error');
  var statusSpan = document.getElementById('query-status');
  var resultsTable = document.getElementById('results-table');

  errorDiv.style.display = 'none';
  statusSpan.textContent = 'Running...';

  try {
    var startTime = performance.now();
    var results = db.exec(sql);
    var elapsed = (performance.now() - startTime).toFixed(1);

    if (results.length === 0) {
      resultsTable.innerHTML = '<tr><td>Query executed successfully. No results returned.</td></tr>';
      statusSpan.textContent = 'Done (' + elapsed + 'ms)';
      return;
    }

    var result = results[0];
    var rowCount = result.values.length;
    statusSpan.textContent = rowCount + ' rows (' + elapsed + 'ms)';

    // Build table HTML
    var html = '<thead><tr>';
    result.columns.forEach(function(col) {
      html += '<th>' + escapeHtml(col) + '</th>';
    });
    html += '</tr></thead><tbody>';

    // Limit display to 1000 rows for performance
    var displayRows = Math.min(rowCount, 1000);
    for (var i = 0; i < displayRows; i++) {
      html += '<tr>';
      result.values[i].forEach(function(val) {
        html += '<td>' + escapeHtml(val === null ? 'NULL' : String(val)) + '</td>';
      });
      html += '</tr>';
    }
    html += '</tbody>';

    if (rowCount > 1000) {
      html += '<tfoot><tr><td colspan="' + result.columns.length + '">' +
              'Showing first 1000 of ' + rowCount + ' rows</td></tr></tfoot>';
    }

    resultsTable.innerHTML = html;

  } catch (err) {
    errorDiv.textContent = 'SQL Error: ' + err.message;
    errorDiv.style.display = 'block';
    statusSpan.textContent = 'Error';
    resultsTable.innerHTML = '';
  }
}

function escapeHtml(text) {
  var div = document.createElement('div');
  div.textContent = text;
  return div.innerHTML;
}

function loadExample(element) {
  document.getElementById('sql-editor').value = element.textContent.trim();
  runQuery();
  // Scroll to results
  document.getElementById('query-panel').scrollIntoView({ behavior: 'smooth' });
}

// Keyboard shortcut: Ctrl+Enter to run query
document.addEventListener('keydown', function(e) {
  if (e.ctrlKey && e.key === 'Enter') {
    runQuery();
  }
});

// Initialize on page load
document.addEventListener('DOMContentLoaded', initDatabase);
</script>
