---
title: "`r params$planet_name` Spawn Map"
output:
  html_document:
    includes:
      after_body: footer.html
params:
  planet_name: "tatooine"
---

```{r setup, include=FALSE}
library(leaflet)
library(dplyr)
library(readr)
library(htmltools)

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

# Load data
zones <- read_csv("zones.csv", show_col_types = FALSE)
static_spawns <- read_csv("static_spawns.csv", show_col_types = FALSE)
lair_spawn_groups <- read_csv("lair_spawn_groups.csv", show_col_types = FALSE)
lair_mobiles <- read_csv("lair_mobiles.csv", show_col_types = FALSE)

# Planet name mapping for data vs image files
planet_data_name <- params$planet_name
planet_display_name <- tools::toTitleCase(params$planet_name)

# Handle yavin/yavin4 mismatch
if (planet_data_name == "yavin4") {
  zones_planet_name <- "yavin"
} else {
  zones_planet_name <- planet_data_name
}

# Second-tier spawn analysis: expected abundance & concentration of each
# creature per region, plus overlapping-zone intersection pieces.
source("spawn_analysis.R")
spawn_model <- build_planet_spawn_model(
  zones_planet_name,
  data = list(zones = zones, groups = lair_spawn_groups, mobiles = lair_mobiles)
)

# Map image paths - relative to html/maps/ output directory
image_map <- list(
  corellia = "Corellia.jpg",
  dantooine = "Dantooine.jpg",
  dathomir = "Dathomir.jpg",
  endor = "Endor.jpg",
  lok = "Lok.jpg",
  naboo = "Naboo.jpg",
  rori = "Rori.webp",
  talus = "talus_map.png",
  tatooine = "Tatooine.jpg",
  yavin4 = "Yavin4.jpg"
)

map_image <- image_map[[planet_data_name]]

# Filter data for this planet
planet_zones <- zones %>%
  filter(planet == zones_planet_name, !is.na(spawnZone), spawnZone != "")

planet_static_all <- static_spawns %>%
  filter(zone_id == planet_data_name)

# Interior spawns (parent_id != 0) live inside cells (caves, buildings) and
# their x/z/y are relative to that cell, not the world. Placing them on the
# planet map produces a bogus cluster near (0,0), so draw world spawns only.
planet_static <- planet_static_all %>% filter(parent_id == 0)
n_interior_excluded <- nrow(planet_static_all) - nrow(planet_static)

# Get creatures for each spawn zone (truncated for popup)
get_creatures_for_zone <- function(spawn_zone) {
  lairs <- lair_spawn_groups %>%
    filter(spawnGroupName == spawn_zone) %>%
    pull(lairTemplateName)

  creatures <- lair_mobiles %>%
    filter(lairName %in% lairs) %>%
    distinct(creatureName) %>%
    pull(creatureName)

  if (length(creatures) == 0) return("No creatures")
  if (length(creatures) > 10) {
    return(paste(c(head(creatures, 10), paste0("... and ", length(creatures) - 10, " more")), collapse = ", "))
  }
  paste(creatures, collapse = ", ")
}

# Get ALL creatures for each spawn zone (for sidebar)
get_all_creatures_for_zone <- function(spawn_zone) {
  lairs <- lair_spawn_groups %>%
    filter(spawnGroupName == spawn_zone) %>%
    pull(lairTemplateName)

  creatures <- lair_mobiles %>%
    filter(lairName %in% lairs) %>%
    distinct(creatureName) %>%
    arrange(creatureName) %>%
    pull(creatureName)

  if (length(creatures) == 0) return(list())
  as.list(creatures)
}

# Build zone data for sidebar
zone_data_for_sidebar <- lapply(seq_len(nrow(planet_zones)), function(i) {
  zone <- planet_zones[i, ]
  list(
    name = zone$spawnZone,
    type = zone$zoneType,
    x = zone$x,
    y = zone$y,
    x2 = if (!is.na(zone$x2)) zone$x2 else NULL,
    y2 = if (!is.na(zone$y2)) zone$y2 else NULL,
    r = if (!is.na(zone$r)) zone$r else NULL,
    r1 = if (!is.na(zone$r1)) zone$r1 else NULL,
    r2 = if (!is.na(zone$r2)) zone$r2 else NULL,
    creatures = get_all_creatures_for_zone(zone$spawnZone)
  )
})
names(zone_data_for_sidebar) <- planet_zones$spawnZone

# Game coordinate bounds
game_bounds <- list(
  min_x = -8000,
  max_x = 8000,
  min_y = -8000,
  max_y = 8000
)
```

# `r planet_display_name`

This interactive map shows spawn zones and static spawn points for `r planet_display_name`.

- **Blue circles/rectangles**: Dynamic spawn zones (lairs spawn here)
- **Red markers**: Static spawn points (fixed creature locations)
- **Hover** over zones to see zone name
- **Click** on a zone to see full details in the sidebar (including all creatures)
- Use the **layer control** (top right) to toggle visibility
- **Search** for creatures below - zones without matching creatures will be hidden, and the **creature finder** ranks where to find them by abundance and concentration (accounting for zone overlap)

<div id="creature-search-container">
<input type="text" id="creature-search" placeholder="Search creatures (e.g., rancor, *krayt*, gorax...)" />
<span id="search-results-count"></span>
<button id="clear-search" onclick="clearCreatureSearch()">Clear</button>
</div>

<div id="creature-finder">
<div id="finder-header">
  <strong>Where to find <span id="finder-creature">—</span></strong>
  <span id="finder-sort">
    Rank by:
    <button class="finder-sort-btn active" data-metric="concentration" onclick="setFinderMetric('concentration')">Concentration (easiest to find)</button>
    <button class="finder-sort-btn" data-metric="abundance" onclick="setFinderMetric('abundance')">Abundance (most spawns)</button>
  </span>
</div>
<div id="finder-note">Search a creature above to rank spawn zones and zone overlaps by expected <em>abundance</em> (how many you'll find) and <em>concentration</em> (what fraction of nearby lairs are this creature). Click a row to fly the map there.</div>
<table id="finder-table" style="display:none">
  <thead><tr><th>Location</th><th>Zones</th><th class="num">Abundance</th><th class="num">Concentration</th></tr></thead>
  <tbody></tbody>
</table>
</div>

<style>
#creature-search-container {
  margin: 15px 0;
  padding: 10px;
  background: #f5f5f5;
  border-radius: 5px;
}
#creature-finder {
  margin: 15px 0;
  padding: 10px;
  background: #f0f6ff;
  border: 1px solid #cfe0ff;
  border-radius: 5px;
}
#finder-header { display: flex; justify-content: space-between; align-items: center; flex-wrap: wrap; gap: 8px; }
#finder-note { color: #555; font-size: 13px; margin: 6px 0; }
.finder-sort-btn {
  padding: 4px 10px; margin-left: 4px; cursor: pointer; font-size: 12px;
  background: #e0e8f5; border: 1px solid #b8cdf0; border-radius: 4px;
}
.finder-sort-btn.active { background: #3388ff; color: #fff; border-color: #3388ff; }
#finder-table { width: 100%; border-collapse: collapse; font-size: 13px; margin-top: 8px; }
#finder-table th, #finder-table td { text-align: left; padding: 5px 8px; border-bottom: 1px solid #e0e0e0; }
#finder-table th.num, #finder-table td.num { text-align: right; }
#finder-table tbody tr { cursor: pointer; }
#finder-table tbody tr:hover { background: #e8f0ff; }
#finder-table .overlap-row td:first-child { font-style: italic; color: #2a5; }
.finder-bar { display: inline-block; height: 10px; background: #3388ff; border-radius: 2px; vertical-align: middle; margin-left: 6px; }
#creature-search {
  width: 400px;
  padding: 8px 12px;
  font-size: 14px;
  border: 1px solid #ccc;
  border-radius: 4px;
}
#creature-search:focus {
  outline: none;
  border-color: #3388ff;
  box-shadow: 0 0 3px rgba(51,136,255,0.5);
}
#search-results-count {
  margin-left: 10px;
  color: #666;
  font-size: 14px;
}
#clear-search {
  margin-left: 10px;
  padding: 8px 15px;
  cursor: pointer;
  background: #e0e0e0;
  border: 1px solid #ccc;
  border-radius: 4px;
}
#clear-search:hover { background: #d0d0d0; }

#zone-sidebar {
  position: fixed;
  right: 0;
  top: 0;
  width: 320px;
  height: 100vh;
  background: white;
  border-left: 2px solid #ccc;
  padding: 15px;
  overflow-y: auto;
  z-index: 10000;
  box-shadow: -2px 0 5px rgba(0,0,0,0.2);
  display: none;
}
#zone-sidebar.visible { display: block; }
#zone-sidebar h3 { margin-top: 0; color: #333; }
#zone-sidebar .close-btn {
  position: absolute;
  top: 10px;
  right: 10px;
  cursor: pointer;
  font-size: 20px;
  color: #666;
}
#zone-sidebar .close-btn:hover { color: #000; }
#zone-sidebar .creature-list {
  max-height: 400px;
  overflow-y: auto;
  border: 1px solid #ddd;
  padding: 8px;
  margin-top: 10px;
  background: #f9f9f9;
}
#zone-sidebar .creature-list a {
  display: block;
  padding: 2px 0;
  color: #0066cc;
  text-decoration: none;
}
#zone-sidebar .creature-list a:hover { text-decoration: underline; }
#zone-sidebar .zone-info { margin: 10px 0; }
#zone-sidebar .zone-info strong { color: #555; }
</style>

```{r sidebar_html, results='asis', echo=FALSE}
cat('<div id="zone-sidebar"><span class="close-btn" onclick="document.getElementById(\'zone-sidebar\').classList.remove(\'visible\')">&times;</span><h3 id="sidebar-zone-name">Zone Details</h3><div class="zone-info"><p><strong>Type:</strong> <span id="sidebar-zone-type"></span></p><p><strong>Coordinates:</strong> <span id="sidebar-zone-coords"></span></p></div><h4>Creatures (<span id="sidebar-creature-count">0</span>)</h4><div class="creature-list" id="sidebar-creature-list"></div></div>')
```

```{r zone_data_script, results='asis', echo=FALSE}
script_content <- sprintf("
<script>
var zoneDataGlobal = %s;

function showZoneSidebar(zoneName) {
  var data = zoneDataGlobal[zoneName];
  if (!data) {
    console.log('Zone not found:', zoneName, 'Available:', Object.keys(zoneDataGlobal));
    return;
  }

  document.getElementById('sidebar-zone-name').textContent = data.name;
  document.getElementById('sidebar-zone-type').textContent = data.type.charAt(0).toUpperCase() + data.type.slice(1);

  var coords = '';
  if (data.type === 'circle') {
    coords = 'Center: (' + Math.round(data.x) + ', ' + Math.round(data.y) + '), Radius: ' + Math.round(data.r);
  } else if (data.type === 'ring') {
    coords = 'Center: (' + Math.round(data.x) + ', ' + Math.round(data.y) + '), Inner: ' + Math.round(data.r1) + ', Outer: ' + Math.round(data.r2);
  } else {
    coords = '(' + Math.round(data.x) + ', ' + Math.round(data.y) + ') to (' + Math.round(data.x2) + ', ' + Math.round(data.y2) + ')';
  }
  document.getElementById('sidebar-zone-coords').textContent = coords;

  var creatures = data.creatures || [];
  document.getElementById('sidebar-creature-count').textContent = creatures.length;

  var listHtml = '';
  creatures.forEach(function(c) {
    listHtml += '<a href=\"../creatures/' + c + '.html\" target=\"_blank\">' + c + '</a>';
  });
  if (creatures.length === 0) {
    listHtml = '<em>No creatures found</em>';
  }
  document.getElementById('sidebar-creature-list').innerHTML = listHtml;

  document.getElementById('zone-sidebar').classList.add('visible');
}

// Search functionality
var leafletMapGlobal = null;
var allZoneNames = Object.keys(zoneDataGlobal);
var zoneLayers = {}; // Store references to all zone layers

function wildcardToRegex(pattern) {
  // Convert wildcard pattern to regex: * becomes .*, ? becomes .
  // If no wildcards, do substring match (add .* around it)
  if (pattern.indexOf('*') === -1 && pattern.indexOf('?') === -1) {
    return new RegExp(pattern, 'i');
  }
  var escaped = pattern.replace(/[.+^${}()|[\\]\\\\]/g, '\\\\$&');
  escaped = escaped.replace(/\\*/g, '.*').replace(/\\?/g, '.');
  return new RegExp('^' + escaped + '$', 'i');
}

function filterZonesByCreature(searchTerm) {
  if (!leafletMapGlobal || !searchTerm.trim()) {
    // Show all zones if search is empty
    showAllZonesSearch();
    return;
  }

  var regex = wildcardToRegex(searchTerm.trim());
  var matchingZones = [];
  var matchingCreatures = new Set();

  // Find zones that have matching creatures
  allZoneNames.forEach(function(zoneName) {
    var zoneData = zoneDataGlobal[zoneName];
    if (!zoneData || !zoneData.creatures) return;

    var hasMatch = zoneData.creatures.some(function(creature) {
      if (regex.test(creature)) {
        matchingCreatures.add(creature);
        return true;
      }
      return false;
    });

    if (hasMatch) {
      matchingZones.push(zoneName);
    }
  });

  // Show/hide zones on the map using stored layer references
  Object.keys(zoneLayers).forEach(function(zoneName) {
    var show = matchingZones.includes(zoneName);
    zoneLayers[zoneName].forEach(function(layer) {
      if (show) {
        if (!leafletMapGlobal.hasLayer(layer)) leafletMapGlobal.addLayer(layer);
      } else {
        if (leafletMapGlobal.hasLayer(layer)) leafletMapGlobal.removeLayer(layer);
      }
    });
  });

  // Update checkboxes in layer control
  var checkboxes = document.querySelectorAll('.leaflet-control-layers-overlays input');
  checkboxes.forEach(function(cb) {
    var label = cb.nextSibling.textContent.trim();
    if (zoneDataGlobal[label]) {
      cb.checked = matchingZones.includes(label);
    }
  });

  // Update results count
  document.getElementById('search-results-count').textContent =
    matchingZones.length + ' zones, ' + matchingCreatures.size + ' creatures';
}

function showAllZonesSearch() {
  if (!leafletMapGlobal) return;

  // Use stored layer references to show all zones
  Object.keys(zoneLayers).forEach(function(zoneName) {
    zoneLayers[zoneName].forEach(function(layer) {
      if (!leafletMapGlobal.hasLayer(layer)) leafletMapGlobal.addLayer(layer);
    });
  });

  // Update checkboxes
  var checkboxes = document.querySelectorAll('.leaflet-control-layers-overlays input');
  checkboxes.forEach(function(cb) {
    var label = cb.nextSibling.textContent.trim();
    if (zoneDataGlobal[label]) {
      cb.checked = true;
    }
  });

  document.getElementById('search-results-count').textContent = '';
}

function clearCreatureSearch() {
  document.getElementById('creature-search').value = '';
  showAllZonesSearch();
}

// Set up search input listener when DOM is ready
document.addEventListener('DOMContentLoaded', function() {
  var searchInput = document.getElementById('creature-search');
  if (searchInput) {
    var debounceTimer;
    searchInput.addEventListener('input', function() {
      clearTimeout(debounceTimer);
      debounceTimer = setTimeout(function() {
        filterZonesByCreature(searchInput.value);
        if (typeof updateCreatureFinder === 'function') updateCreatureFinder(searchInput.value);
      }, 200);
    });
  }
});
</script>
", jsonlite::toJSON(zone_data_for_sidebar, auto_unbox = TRUE))
cat(script_content)
```

```{r spawn_finder_script, results='asis', echo=FALSE}
# Embed the per-planet spawn model and the client-side creature finder.
strip_prefix <- function(x) sub("^@[^:]*:", "", x)

regions_json <- if (nrow(spawn_model$regions) > 0) {
  jsonlite::toJSON(spawn_model$regions %>%
    transmute(id = region_id, name = strip_prefix(name),
              cx = round(cx, 1), cy = round(cy, 1), type = zoneType,
              isWorld = is_world,
              limit = as.numeric(maxSpawnLimit), etot = round(expected_total, 2)),
    dataframe = "rows", auto_unbox = TRUE)
} else "[]"

rc_json <- if (nrow(spawn_model$region_creature) > 0) {
  jsonlite::toJSON(spawn_model$region_creature %>%
    transmute(r = region_id, c = creatureName, a = round(abundance, 3)),
    dataframe = "rows", auto_unbox = TRUE)
} else "[]"

pieces_json <- if (nrow(spawn_model$pieces) > 0) {
  jsonlite::toJSON(spawn_model$pieces %>%
    transmute(ids = member_region_ids, cx = round(cx, 1), cy = round(cy, 1),
              n = n_overlap, total = round(combined_expected_total, 2)),
    dataframe = "rows", auto_unbox = TRUE)
} else "[]"

finder_js <- sprintf("
<script>
var spawnRegions = %s;   // [{id,name,cx,cy,type,isWorld,limit,etot}]
var spawnRC = %s;        // [{r,c,a}]
var spawnPieces = %s;    // [{ids:[...],cx,cy,n,total}]

// Index region metadata by id and build creature -> {region_id: abundance}.
var regionById = {};
spawnRegions.forEach(function(reg) { regionById[reg.id] = reg; });
var creatureAbundance = {};
spawnRC.forEach(function(row) {
  if (!creatureAbundance[row.c]) creatureAbundance[row.c] = {};
  creatureAbundance[row.c][row.r] = row.a;
});
var allCreatureNames = Object.keys(creatureAbundance);

var finderMetric = 'concentration';
var finderLastQuery = '';

// The creatures people hunt are rare, so sub-1%% concentrations carry the real
// signal. Show 2 significant figures below the readable-decimal range instead
// of rounding rare cases to 0.
function formatPct(frac) {
  var p = frac * 100;
  if (p <= 0) return '0%%';
  if (p >= 1) return p.toFixed(1) + '%%';
  return parseFloat(p.toPrecision(2)) + '%%';
}
function formatAbund(v) {
  if (v <= 0) return '0';
  if (v >= 10) return v.toFixed(0);
  if (v >= 1) return v.toFixed(1);
  return String(parseFloat(v.toPrecision(2)));
}

function setFinderMetric(metric) {
  finderMetric = metric;
  document.querySelectorAll('.finder-sort-btn').forEach(function(b) {
    b.classList.toggle('active', b.getAttribute('data-metric') === metric);
  });
  updateCreatureFinder(finderLastQuery);
}

function updateCreatureFinder(query) {
  finderLastQuery = query || '';
  var table = document.getElementById('finder-table');
  var note = document.getElementById('finder-note');
  var label = document.getElementById('finder-creature');
  var tbody = table.querySelector('tbody');
  tbody.innerHTML = '';

  var q = finderLastQuery.trim().toLowerCase().replace(/[*?]/g, '');
  if (!q) {
    label.textContent = '—';
    table.style.display = 'none';
    note.style.display = 'block';
    return;
  }

  // Aggregate abundance over every creature whose name contains the query.
  var matched = allCreatureNames.filter(function(c) { return c.toLowerCase().indexOf(q) !== -1; });
  var ab = {};   // region_id -> summed abundance
  matched.forEach(function(c) {
    var m = creatureAbundance[c];
    Object.keys(m).forEach(function(rid) { ab[rid] = (ab[rid] || 0) + m[rid]; });
  });

  label.textContent = query + (matched.length > 1 ? ' (' + matched.length + ' creatures)' : '');

  if (Object.keys(ab).length === 0) {
    note.textContent = 'No spawn-zone data for \"' + query + '\" on this planet.';
    note.style.display = 'block';
    table.style.display = 'none';
    return;
  }

  var rows = [];
  // Single regions
  Object.keys(ab).forEach(function(rid) {
    var reg = regionById[rid];
    if (!reg) return;
    var abundance = ab[rid];
    rows.push({
      label: reg.name + (reg.isWorld ? ' (planet-wide)' : ''),
      zones: 1, overlap: false, cx: reg.cx, cy: reg.cy,
      abundance: abundance,
      concentration: reg.etot > 0 ? abundance / reg.etot : 0
    });
  });
  // Zone overlaps (intersection pieces)
  spawnPieces.forEach(function(pc) {
    var sum = 0, names = [], any = false;
    pc.ids.forEach(function(rid) {
      if (ab[rid] != null) { sum += ab[rid]; any = true; }
      if (regionById[rid]) names.push(regionById[rid].name);
    });
    if (!any) return;
    rows.push({
      label: names.join(' ∩ '),
      zones: pc.n, overlap: true, cx: pc.cx, cy: pc.cy,
      abundance: sum,
      concentration: pc.total > 0 ? sum / pc.total : 0
    });
  });

  rows.sort(function(a, b) { return b[finderMetric] - a[finderMetric]; });
  rows = rows.slice(0, 25);

  var maxVal = rows.length ? rows[0][finderMetric] : 1;
  rows.forEach(function(row) {
    var tr = document.createElement('tr');
    if (row.overlap) tr.className = 'overlap-row';
    var barW = Math.round(60 * (row[finderMetric] / (maxVal || 1)));
    tr.innerHTML =
      '<td>' + row.label + '</td>' +
      '<td>' + (row.overlap ? row.zones + '×' : 'zone') + '</td>' +
      '<td class=\"num\">' + formatAbund(row.abundance) +
        (finderMetric === 'abundance' ? '<span class=\"finder-bar\" style=\"width:' + barW + 'px\"></span>' : '') + '</td>' +
      '<td class=\"num\">' + formatPct(row.concentration) +
        (finderMetric === 'concentration' ? '<span class=\"finder-bar\" style=\"width:' + barW + 'px\"></span>' : '') + '</td>';
    tr.onclick = function() {
      if (typeof leafletMapGlobal !== 'undefined' && leafletMapGlobal) {
        leafletMapGlobal.setView([row.cy, row.cx], 1);
        if (window._finderMarker) leafletMapGlobal.removeLayer(window._finderMarker);
        window._finderMarker = L.circleMarker([row.cy, row.cx],
          { radius: 12, color: '#ff9500', weight: 3, fill: false }).addTo(leafletMapGlobal);
      }
    };
    tbody.appendChild(tr);
  });

  note.style.display = 'none';
  table.style.display = 'table';
}
</script>
", regions_json, rc_json, pieces_json)
cat(finder_js)
```

```{r map, fig.width=10, fig.height=10}
# Create the leaflet map with simple CRS (game coordinates)
map <- leaflet(options = leafletOptions(
  crs = leafletCRS(crsClass = "L.CRS.Simple"),
  minZoom = -5,
  maxZoom = 4
)) %>%
  # Set view to center of map, zoomed out to see full planet
  setView(lng = 0, lat = 0, zoom = -2) %>%
  # Add the planet image as background via JavaScript
  htmlwidgets::onRender(sprintf("
    function(el, x) {
      var map = this;
      var imageUrl = '%s';
      var bounds = [[%d, %d], [%d, %d]];
      L.imageOverlay(imageUrl, bounds).addTo(map);
    }
  ", map_image, game_bounds$min_y, game_bounds$min_x, game_bounds$max_y, game_bounds$max_x))

# Track all zone names for layer control
zone_names <- c()

# Add circular zones - each zone gets its own layer group
circle_zones <- planet_zones %>% filter(zoneType == "circle", !is.na(r))
if (nrow(circle_zones) > 0) {
  for (i in 1:nrow(circle_zones)) {
    zone <- circle_zones[i, ]
    creatures <- get_creatures_for_zone(zone$spawnZone)
    zone_names <- c(zone_names, zone$spawnZone)

    popup_content <- paste0(
      "<b>", zone$spawnZone, "</b><br>",
      "<b>Type:</b> Circle<br>",
      "<b>Center:</b> (", round(zone$x), ", ", round(zone$y), ")<br>",
      "<b>Radius:</b> ", round(zone$r), "<br>",
      "<b>Creatures:</b> ", creatures, "<br><br>",
      "<button onclick=\"showZoneSidebar('", zone$spawnZone, "')\" style=\"cursor:pointer;padding:5px 10px;\">View All Creatures</button>"
    )

    map <- map %>%
      addCircles(
        lng = zone$x,
        lat = zone$y,
        radius = zone$r,
        color = "#3388ff",
        fillColor = "#3388ff",
        fillOpacity = 0.2,
        weight = 2,
        popup = popup_content,
        label = zone$spawnZone,
        group = zone$spawnZone,
        # layerId must be globally unique: duplicate ids make Leaflet drop the
        # earlier shape, so same-named regions would not all draw. Keep `group`
        # as the zone name so duplicates still share one layer-control toggle.
        layerId = paste0("circle_", i)
      )
  }
}

# Add rectangular zones - each zone gets its own layer group
rect_zones <- planet_zones %>% filter(zoneType == "rectangle", !is.na(x2), !is.na(y2))
if (nrow(rect_zones) > 0) {
  for (i in 1:nrow(rect_zones)) {
    zone <- rect_zones[i, ]
    creatures <- get_creatures_for_zone(zone$spawnZone)
    zone_names <- c(zone_names, zone$spawnZone)

    popup_content <- paste0(
      "<b>", zone$spawnZone, "</b><br>",
      "<b>Type:</b> Rectangle<br>",
      "<b>Bounds:</b> (", round(zone$x), ", ", round(zone$y), ") to (",
      round(zone$x2), ", ", round(zone$y2), ")<br>",
      "<b>Creatures:</b> ", creatures, "<br><br>",
      "<button onclick=\"showZoneSidebar('", zone$spawnZone, "')\" style=\"cursor:pointer;padding:5px 10px;\">View All Creatures</button>"
    )

    map <- map %>%
      addRectangles(
        lng1 = zone$x,
        lat1 = zone$y,
        lng2 = zone$x2,
        lat2 = zone$y2,
        color = "#3388ff",
        fillColor = "#3388ff",
        fillOpacity = 0.2,
        weight = 2,
        popup = popup_content,
        label = zone$spawnZone,
        group = zone$spawnZone,
        layerId = paste0("rect_", i)
      )
  }
}

# Add ring zones (e.g. "medium newbie" rings around starter cities). A ring is
# an annulus between an inner radius (r1) and outer radius (r2); Leaflet has no
# annulus primitive, so draw a filled outer circle plus an unfilled inner circle
# to mark the hole. Both shapes share the zone-name group so they toggle as one.
ring_zones <- planet_zones %>% filter(zoneType == "ring", !is.na(r1), !is.na(r2))
if (nrow(ring_zones) > 0) {
  for (i in 1:nrow(ring_zones)) {
    zone <- ring_zones[i, ]
    creatures <- get_creatures_for_zone(zone$spawnZone)
    zone_names <- c(zone_names, zone$spawnZone)

    popup_content <- paste0(
      "<b>", zone$spawnZone, "</b><br>",
      "<b>Type:</b> Ring<br>",
      "<b>Center:</b> (", round(zone$x), ", ", round(zone$y), ")<br>",
      "<b>Inner radius:</b> ", round(zone$r1), "<br>",
      "<b>Outer radius:</b> ", round(zone$r2), "<br>",
      "<b>Creatures:</b> ", creatures, "<br><br>",
      "<button onclick=\"showZoneSidebar('", zone$spawnZone, "')\" style=\"cursor:pointer;padding:5px 10px;\">View All Creatures</button>"
    )

    map <- map %>%
      addCircles(
        lng = zone$x, lat = zone$y, radius = zone$r2,
        color = "#3388ff", fillColor = "#3388ff", fillOpacity = 0.2, weight = 2,
        popup = popup_content, label = zone$spawnZone,
        group = zone$spawnZone, layerId = paste0("ring_outer_", i)
      ) %>%
      addCircles(
        lng = zone$x, lat = zone$y, radius = zone$r1,
        color = "#3388ff", fillColor = "#ffffff", fillOpacity = 0.0, weight = 1,
        group = zone$spawnZone, layerId = paste0("ring_inner_", i)
      )
  }
}

# Add static spawn markers
n_static_sampled <- 0
if (nrow(planet_static) > 0) {
  # Limit markers if there are too many (for performance)
  static_to_show <- if (nrow(planet_static) > 500) {
    set.seed(42)  # stable subset across renders
    n_static_sampled <- 500
    planet_static %>% sample_n(500)
  } else {
    planet_static
  }

  for (i in 1:nrow(static_to_show)) {
    spawn <- static_to_show[i, ]

    popup_content <- paste0(
      "<b>", spawn$mobile, "</b><br>",
      "<b>Location:</b> (", round(spawn$x), ", ", round(spawn$y), ", ", round(spawn$z), ")<br>",
      "<b>Respawn:</b> ", spawn$respawn_time, "s"
    )

    map <- map %>%
      addCircleMarkers(
        lng = spawn$x,
        lat = spawn$y,
        radius = 4,
        color = "#ff4444",
        fillColor = "#ff4444",
        fillOpacity = 0.8,
        weight = 1,
        popup = popup_content,
        label = spawn$mobile,
        group = "Static Spawns"
      )
  }
}

# Add layer control with all individual zones + static spawns
# Sort zone names alphabetically for easier navigation
sorted_zones <- sort(unique(zone_names))
all_layers <- c(sorted_zones, "Static Spawns")

map <- map %>%
  addLayersControl(
    overlayGroups = all_layers,
    options = layersControlOptions(collapsed = TRUE)
  ) %>%
  # Add check/uncheck all buttons and click handlers via JavaScript

  htmlwidgets::onRender(sprintf("
    function(el, x) {
      var map = this;
      var zoneNames = %s;

      // Store map reference globally for search functionality
      leafletMapGlobal = map;

      // Store references to all zone layers for show/hide functionality.
      // A single zone name can map to several shapes (duplicate-named regions
      // and the two circles of a ring), so each name holds an array of layers.
      map.eachLayer(function(layer) {
        if (layer.options && layer.options.group && zoneDataGlobal[layer.options.group]) {
          var g = layer.options.group;
          if (!zoneLayers[g]) zoneLayers[g] = [];
          zoneLayers[g].push(layer);
        }
      });

      // Create control container for buttons
      var container = L.DomUtil.create('div', 'leaflet-bar leaflet-control');
      container.style.backgroundColor = 'white';
      container.style.padding = '5px';

      // Show All button
      var showBtn = L.DomUtil.create('button', '', container);
      showBtn.innerHTML = 'Show All Zones';
      showBtn.style.display = 'block';
      showBtn.style.marginBottom = '3px';
      showBtn.style.cursor = 'pointer';
      showBtn.onclick = function() {
        // Use stored layer references
        Object.keys(zoneLayers).forEach(function(name) {
          zoneLayers[name].forEach(function(layer) {
            if (!map.hasLayer(layer)) map.addLayer(layer);
          });
        });
        // Update checkboxes in layer control
        var checkboxes = document.querySelectorAll('.leaflet-control-layers-overlays input');
        checkboxes.forEach(function(cb) {
          var label = cb.nextSibling.textContent.trim();
          if (zoneLayers[label]) cb.checked = true;
        });
        // Clear search box
        document.getElementById('creature-search').value = '';
        document.getElementById('search-results-count').textContent = '';
      };

      // Hide All button
      var hideBtn = L.DomUtil.create('button', '', container);
      hideBtn.innerHTML = 'Hide All Zones';
      hideBtn.style.display = 'block';
      hideBtn.style.cursor = 'pointer';
      hideBtn.onclick = function() {
        // Use stored layer references
        Object.keys(zoneLayers).forEach(function(name) {
          zoneLayers[name].forEach(function(layer) {
            if (map.hasLayer(layer)) map.removeLayer(layer);
          });
        });
        // Update checkboxes in layer control
        var checkboxes = document.querySelectorAll('.leaflet-control-layers-overlays input');
        checkboxes.forEach(function(cb) {
          var label = cb.nextSibling.textContent.trim();
          if (zoneLayers[label]) cb.checked = false;
        });
      };

      // Add as custom control
      var CustomControl = L.Control.extend({
        options: { position: 'topright' },
        onAdd: function(map) { return container; }
      });
      map.addControl(new CustomControl());
    }
  ", jsonlite::toJSON(sorted_zones)))

map
```

```{r map_notes, results='asis', echo=FALSE}
notes <- c()
if (n_interior_excluded > 0) {
  notes <- c(notes, sprintf(
    "%d interior static spawn(s) (inside caves/buildings) are omitted from the map because their coordinates are relative to the cell, not the world.",
    n_interior_excluded))
}
if (n_static_sampled > 0) {
  notes <- c(notes, sprintf(
    "Showing a random sample of %d static spawns (of %d world spawns) for performance; the Static Spawn Summary below counts all of them.",
    n_static_sampled, nrow(planet_static)))
}
if (length(notes) > 0) {
  cat(paste0("> **Note:** ", notes, collapse = "\n>\n"), "\n")
}
```

## Zone Summary

```{r zone_table}
if (nrow(planet_zones) > 0) {
  zone_summary <- planet_zones %>%
    select(spawnZone, zoneType, x, y, x2, y2, r) %>%
    arrange(spawnZone)

  DT::datatable(zone_summary,
                filter = "top",
                options = list(
                  pageLength = 15,
                  dom = "ftip"
                ),
                rownames = FALSE)
} else {
  cat("No spawn zones found for this planet.")
}
```

## Static Spawn Summary

```{r static_table}
if (nrow(planet_static) > 0) {
  static_summary <- planet_static %>%
    group_by(mobile) %>%
    summarise(count = n(), .groups = "drop") %>%
    arrange(desc(count))

  DT::datatable(static_summary,
                filter = "top",
                options = list(
                  pageLength = 15,
                  dom = "ftip"
                ),
                rownames = FALSE)
} else {
  cat("No static spawns found for this planet.")
}
```
